Synpotic Soil Characterization

### 2023-03-11 3-reports/characterization_report.Rmd
update graphs
process and plot xrd
WRC and texture functions
update markdown report

```{r correlations-all, fig.height=7, fig.width=7}
tar_read(gg_correlations)$corr_all
```

@@

>>>>

```{r correlations-all, fig.height=8, fig.width=8}
tar_read(gg_correlations)$corr_all
```

@@

## XRD
```{r xrd, fig.height=4, fig.width=15}
tar_read(gg_xrd)
```

## Soil Physics

### WRC

```{r wrc, fig.height=7, fig.width=8}
tar_read(gg_wrc)

### Texture
```{r texture}
tar_read(gg_texture)
```
